% =====================================================================
% 11_synthesis.tex — load-bearing assumptions, connection to the three
% target empirical facts, roadmap of reconstruction flags (WP-E)
% =====================================================================
\section{Synthesis: what drives each result, and the connection to the empirical facts}
\label{sec:synthesis}

This closing section does three things. First, it maps each major analytical
result to the assumption(s) that are \emph{load-bearing} for it --- the conditions
without which the result fails or changes sign --- and states what breaks if each
is relaxed. Second, it ties the analytical results to the paper's three target
empirical facts. Third, it indexes every reconstruction flag in the document, so
that a reader (or the big\_cy extension worker) can locate exactly where KL's
published derivation was terse and the algebra had to be filled in.

\subsection{Load-bearing assumptions}
\label{sec:load-bearing}

Table~\ref{tab:load-bearing} maps the results to their load-bearing assumptions.
The entries are deliberately conservative: an assumption is listed as load-bearing
for a result only if relaxing it overturns or qualitatively changes that result,
not merely if it appears in the proof. Throughout, ``Prop.~$n$'' refers to the
propositions of this document
(Propositions~\ref{prop:prices}--\ref{prop:riskpremium}), ``ERS/LOOP'' to the
efficient-risk-sharing / law-of-one-price relation of
Subsection~\ref{sec:loop}, and ``Special.'' to the specialness arguments of
Subsection~\ref{sec:specialness}.

\begin{longtable}{p{0.20\textwidth} p{0.30\textwidth} p{0.42\textwidth}}
\caption{Load-bearing assumptions, by result.}\label{tab:load-bearing}\\
\toprule
\textbf{Assumption} & \textbf{Results it is load-bearing for} & \textbf{What breaks if relaxed}\\
\midrule
\endfirsthead
\multicolumn{3}{c}{\emph{(Table~\ref{tab:load-bearing}, continued)}}\\
\toprule
\textbf{Assumption} & \textbf{Results it is load-bearing for} & \textbf{What breaks if relaxed}\\
\midrule
\endhead
\bottomrule
\endfoot

\textbf{Nominal rigidity} (sticky wages, or sticky prices in B.5)
& Prop.~\ref{prop:prices} (recession), Prop.~\ref{prop:returns}
(realized-return responses), Prop.~\ref{prop:wealth} (revaluation),
Special.~(zero net supply)
& Without it, a safety shock moves only \emph{prices}, not quantities: under
flexible wages/prices the Home CPI and real rate fall but employment, the real
exchange rate, and output are unchanged (Prop.~\ref{prop:prices}, flexible-wage
branch~\eqref{eq:flex-labor}). No Keynesian recession; the dollar's real
appreciation in bad times and the whole propagation mechanism vanish.\\

\textbf{Taylor rule does not cut rates one-for-one with $\cy$}
(finite $\taylor$, no seigniorage offset)
& Prop.~\ref{prop:prices}, Prop.~\ref{prop:returns}
& The nonneutrality of safety shocks requires that monetary policy not undo the
convenience-yield wedge~\eqref{eq:euler-r}. If the central bank cut $\inom$
one-for-one with $\cy$ (and ignored seigniorage, with flexible-wage efficiency),
it would fully neutralize the safety shock --- no real-rate wedge, no recession
(KL p.~1668, ``Monetary Policy Response''). Any rule that does not respond with a
\emph{unitary} coefficient on the safety shock preserves the result; this holds
for conventional Taylor rules in the US/G10.\\

\textbf{Complete home bias} $\hbias\to\zs/(1+\zs)$
& Clean statements of Props.~\ref{prop:prices}--\ref{prop:wealth} (the
$\dev{\wsh}_1=0$, $\Eone\dev{\wsh}_2=0$ benchmark) and of
Props.~\ref{prop:portfolios}--\ref{prop:riskpremium} (symmetric-portfolio point)
& At complete home bias $\hbias\frac{1+\zs}{\zs}=1$, so the relative-price loading
is unity and $\theta$-feedback terms collapse, giving $\dev{\wsh}_1=0$ and a clean
$\theta$-benchmark. Away from it, Foreign output also responds (the
$(\tel-1)(1-(\hbias\frac{1+\zs}{\zs})^2)$ terms in~\eqref{eq:Ewsh-solved} and
\eqref{eq:eq99} reactivate), the wealth share moves even at $\rra=\rraF$, and the
propositions hold only ``at least around'' the benchmark.\\

\textbf{Risk-tolerance heterogeneity} $\rra\neq\rraF$
& Prop.~\ref{prop:portfolios}(b) (equity tilt), Prop.~\ref{prop:riskpremium}(a)
(productivity component of the premium)
& Needed for the \emph{levered, equity-tilted} US portfolio
($dk/d[\rraF/\rra]>0$) and for the $\rra-\rraF$ component of the Foreign-bond
premium. \emph{Not} needed for the asset-price propagation of
Props.~\ref{prop:prices}--\ref{prop:returns}, nor for the \emph{positive}
Foreign-bond premium from volatile safety shocks (Prop.~\ref{prop:riskpremium}(b),
the $(\sigma^{\cy})^2$ coefficient, which is positive independent of
$\rra$ vs.~$\rraF$). This separation --- safety-shock propagation and the
Foreign-bond risk premium do not require risk-tolerance heterogeneity, whereas
the levered, equity-tilted US portfolio does --- is one of KL's central
analytical findings.\\

\textbf{Zero net supply of safe bonds} (bond, not equity, convenience)
& Special.~(zero net supply), and implicitly the contractionary sign in
Prop.~\ref{prop:prices}
& If the convenience demand were for capital (positive net supply, priced asset),
a flight to safety would \emph{stimulate} output --- raising $\qk$, wealth,
consumption, and (with variable capital) investment. The Keynesian-recession sign
is specific to the demanded asset being in zero net supply (KL p.~1666; the
bond-vs-equity distinction of Koijen--Yogo 2020).\\

\textbf{Trade elasticity} $\tel$ (size, and $\tel\neq1$)
& ERS/LOOP (magnitude of the $\dev{\rer}$ response,~\eqref{eq:loop-solved}),
Prop.~\ref{prop:wealth} (the $(\tel-1)$ wealth-share channel)
& $\tel$ governs the size of the real-exchange-rate / terms-of-trade response to a
given relative-output gap. At $\tel=1$ (Cobb--Douglas trade) the wealth-share
revaluation channel through expenditure switching vanishes
(the $(\tel-1)$ factor in~\eqref{eq:Ewsh-solved}); the ERS/LOOP relation still
holds but with a different (smaller) exchange-rate sensitivity.\\

\textbf{Positive steady-state labor wedge} $\lwedge>0$
& Prop.~\ref{prop:portfolios}(b) sign of $db_H/d[\rraF/\rra]$,
Prop.~\ref{prop:riskpremium} (the employment channel in the kernel)
& With $\lwedge=0$, employment drops out of the pricing kernel (the
$\lwedge(1-\disc)(1-\cshare)\dev{\ell}_1$ term in~\eqref{eq:v1}/\eqref{eq:m01-home}
vanishes), so aggregate employment is no longer a priced state. The
risk-tolerance comparative static $db_H/d[\rraF/\rra]<0$ relies on $\lwedge>0$
(KL state ``assumes $\lwedge>0$''), and the mechanism by which risk-tolerant
agents insure risk-averse agents against low-employment states requires the wedge
(KL footnote~13: ``only in this case will risk-tolerant agents insure risk-averse
agents against states of the world in which labor falls'').\\

\textbf{Local completeness} (one more asset than shocks)
& Prop.~\ref{prop:portfolios}, Prop.~\ref{prop:riskpremium}, ERS/LOOP, the
Foreign-only robustness (B.4)
& The Devereux--Sutherland portfolio is the efficient one, and the risk-sharing
condition~\eqref{eq:risk-sharing} holds, only because three assets span the two
shocks plus the redistributive margin. With incomplete markets the portfolio is
not pinned down by efficient risk sharing and the kernel-equality relation fails;
the risk-premium decomposition of Prop.~\ref{prop:riskpremium} would no longer be
covariance-with-any-agent's-kernel.\\

\end{longtable}

\paragraph{Reading the table.} Two groupings are worth emphasizing. (i) The
\emph{propagation} results (Props.~\ref{prop:prices}--\ref{prop:returns}: the
recession, the real-rate wedge, the dollar's real appreciation in bad times) rest
on \emph{nominal rigidity}, the \emph{non-neutralizing Taylor rule}, and \emph{zero
net supply}; they do \emph{not} require any risk-tolerance asymmetry. (ii) The
\emph{portfolio and premium} results split: the levered, equity-tilted US balance
sheet (Prop.~\ref{prop:portfolios}(b)) and the $\rra-\rraF$ component of the
premium (Prop.~\ref{prop:riskpremium}(a)) \emph{do} require $\rra\neq\rraF$,
whereas the positive premium from volatile safety shocks
(Prop.~\ref{prop:riskpremium}(b)) does \emph{not}. This is the precise sense in
which, in KL's own structure, the dollar's negative beta can be delivered by the
safety channel \emph{alone}, while the equity tilt requires risk-tolerance
heterogeneity.

\subsection{Connection to the three target empirical facts}
\label{sec:empirical-facts}

KL organize their analytical results around three facts about the international
financial system. We state KL's account faithfully.

\paragraph{Fact 1: the dollar's negative beta / negative risk premium.} The dollar
is an endogenous \emph{hedge}: safe dollar bonds pay well exactly in bad times.
This is the joint content of Propositions~\ref{prop:returns} and
\ref{prop:riskpremium}. By Proposition~\ref{prop:returns}, a positive safety shock
(a flight to safety, a ``bad'' state with a global employment contraction) makes
the Home real exchange rate appreciate and lowers the Foreign-bond return relative
to the dollar bond. By Proposition~\ref{prop:riskpremium}(b), with sufficiently
volatile safety shocks the dollar therefore appreciates in high-marginal-utility
states, giving safe dollar bonds a \emph{negative} beta and Foreign bonds a
\emph{positive} risk premium. This resolves the reserve-currency paradox of
Maggiori (2017): absent safety shocks (Prop.~\ref{prop:riskpremium}(a)) the dollar
counterfactually appreciates in \emph{good} times whenever Home is more
risk-tolerant, but safety shocks flip the sign, and --- crucially --- they do so
\emph{without} requiring a risk-tolerance asymmetry. The efficient-risk-sharing /
law-of-one-price relation of Subsection~\ref{sec:loop} is the structural reason the
dollar appreciation in bad times must coincide with a relative fall in US output.

\paragraph{Fact 2: the US as the world's insurer.} The US loses wealth in a flight
to safety, transferring resources to the rest of the world. This is
Proposition~\ref{prop:wealth}: Home's overall wealth share and net foreign assets
\emph{fall} on a positive safety shock, because Home holds a levered-long-risky,
short-dollar portfolio and the dollar (its liability) appreciates while risky
assets (its assets) underperform. The loss is \emph{partially offset by
seigniorage}: Home, as the issuer of the safe asset whose convenience value
spikes, earns the seigniorage term $-\disc\frac{\zs}{1+\zs}\frac{b^g_{H,s}}{\sav}\dev{\cy}_1$
in the revaluation identity~\eqref{eq:wsh-realized}. Proposition~\ref{prop:portfolios}
adds that \emph{greater US risk tolerance} rationalizes the \emph{disproportionate
equity exposure} of the US external balance sheet ($dk/d[\rraF/\rra]>0$): a
more-risk-tolerant US optimally bears more of the world's equity risk. KL
emphasize (their p.~1665) that ``it is in this sense that greater risk tolerance is
necessary to explain why the United States takes a disproportionate exposure to
equity returns.''

\paragraph{Fact 3: the US external balance sheet / carry.} The US borrows in
dollars to hold capital and Foreign bonds --- a levered position. This is the
content of Proposition~\ref{prop:portfolios}: the equilibrium Home portfolio is
levered long the world-equity claim (capital) and long Foreign bonds, financed by
issuing dollar bonds ($\frac{\qk k}{\sav}>1$, $\frac{b_H}{\sav}<0$). Because safety
shocks induce a negative beta of dollar bonds, the US \emph{borrows more} in dollar
bonds as it grows more risk-tolerant ($db_H/d[\rraF/\rra]<0$), using the dollar's
hedge property to finance its risky, equity-tilted asset position. Two margins are
separated in Proposition~\ref{prop:portfolios}: the supply of safe dollar debt
moves the dollar-bond margin without touching the equity margin
($dk/db^g_{H,s}=0$, $db_H/db^g_{H,s}>0$), while relative risk tolerance moves both.
KL's account ties the carry/balance-sheet facts to the same two risk factors
(productivity and safety) that drive the premium in
Proposition~\ref{prop:riskpremium}.

\subsection{Roadmap of reconstruction flags}
\label{sec:flag-roadmap}

The document contains \texttt{\textbackslash gapflag} reconstruction notes
wherever KL's published derivation is terse and the algebra (or provenance, or
interpretation) had to be supplied. The list below indexes them by section, with a
one-line note on what was reconstructed. The flags mark places where the
derivation goes \emph{beyond} transcription; in every case the displayed result
matches KL's, and the flag records what was filled in.

\begin{itemize}[leftmargin=1.6em,itemsep=2pt]
  \item \textbf{Section~\ref{sec:notation} (notation), 1 flag.} The composite
  coefficient $\atil$ is KL's $\tilde\alpha$ in their eq.~(74) display but
  $\bar\alpha$ in the B.1.1 text; we treat the two as identical and flag the
  naming.

  \item \textbf{Section~\ref{sec:setup} (setup), 1 flag.} KL assert the
  Devereux--Sutherland-selected portfolio coincides with the efficient one in the
  three-asset / two-shock setting (citing Coeurdacier--Gourinchas 2016) without
  proving the span covers the shocks; we state the equivalence as KL assert it and
  flag the explicit verification as belonging to the portfolio engine.

  \item \textbf{Section~\ref{sec:engine} (impulse engine, App.~B.1), 5 flags.}
  (i) The intermediate terms-of-trade form~\eqref{eq:s1-intermediate} (we expand
  the $\fr{\dev{\rs c}}_1$-elimination algebra); (ii) the period-1 consumption
  closed form~\eqref{eq:c1-solved} (we supply the Euler-substitution chain and
  verify the recurring denominator $\Lambda$); (iii) the expected wealth
  share~\eqref{eq:Ewsh-solved} (we supply the $\atil$-cancellation and the
  $(\tel-1)$ channel, flagging the lengthy term-by-term collection); (iv) the
  Foreign inflation reduced form~\eqref{eq:dPstar1} (we fill the one-line
  forward-substitution of $\Eone\dev{\tot}_2$); (v) the realized capital
  return~\eqref{eq:rk1-solved} (we combine the profit and capital-pricing
  linearizations, flagging the $\disc$ vs.~$(1-\disc)$ weight cancellation).

  \item \textbf{Section~\ref{sec:prop1} (Prop.~1), 2 flags.} The
  $\Eone\dev{\wsh}_2=0$ benchmark (two facts: $\dev{\wsh}_1=0$ at identical
  portfolios, and the relative-labor term of~\eqref{eq:Ewsh-solved} vanishing at
  complete home bias); and the labor-block solution
  \eqref{eq:firm-H}--\eqref{eq:firm-F} (we supply the elimination at
  $\hbias\frac{1+\zs}{\zs}=1$).

  \item \textbf{Section~\ref{sec:prop2} (Prop.~2), 2 flags.} The Foreign-bond
  excess-return cancellation (with $\fr{\dev{\ell}}_1=0$, the exact collapse of the
  two pieces); and the use of~\eqref{eq:Eq2}/(76) in the Foreign Euler to obtain
  the wedge result.

  \item \textbf{Section~\ref{sec:prop3} (Prop.~3), 3 flags.} The term-by-term
  linearization of the realized wealth-share law of motion (51) into (92)
  (standard schema supplied); the seigniorage coefficient
  $-\disc\frac{\zs}{1+\zs}\frac{b^g_{H,s}}{\sav}$ interpretation (the RoW
  population share / fraction of safe debt held abroad); and the
  ``portfolios close to the symmetric benchmark'' qualifier (we make explicit why
  it is needed to decouple the realized-return inputs).

  \item \textbf{Section~\ref{sec:portfolio-engine} (portfolio engine, App.~B.2),
  7 flags.} (i) The log-kernel provenance~\eqref{eq:m01} (unit-IES recursive
  kernel); (ii) the value linearization~\eqref{eq:v1} labor coefficient
  $(1-\lwedge)(1-\cshare)$; (iii) the combined value
  line~\eqref{eq:v1-combined} (the tersest collection step in B.2); (iv) the Home
  risk-adjusted kernel~\eqref{eq:m01-home} (mechanical but with the LHS
  $\rra\tel^z\dev{\epsilon}^z_1$ grouping); (v) the Foreign risk-adjusted
  kernel~\eqref{eq:m01-foreign} (Foreign relabeling, $1/\zs$ weights); (vi) the
  local-completeness / risk-sharing condition~\eqref{eq:risk-sharing}
  (Backus--Smith interpretation, why it pins the portfolio); (vii) the
  international-portfolio equation~\eqref{eq:eq99} and $\Gam$~\eqref{eq:Gamma-def}
  (the densest derivation in B.2 --- a genuine reconstruction of the
  kernel-difference algebra and the identification of the $\Gam$ bracket).

  \item \textbf{Section~\ref{sec:prop4} (Prop.~4), 6 flags.} The
  arbitrary-portfolio labor solutions~\eqref{eq:lab-sym}--\eqref{eq:lab-rel}
  (transcribed); the eq.~(99)-with-$\Gamp$
  identity~\eqref{eq:eq99-prime}--\eqref{eq:Gamma-prime-def} (substitution and the
  $\Gamp$ augmentation); the symmetric-portfolio wealth-share
  expression~\eqref{eq:wsh-final}--\eqref{eq:Delta-def} (the $\Delta$
  normalization); the Prop.~4 statement (transcribed from the brief, main paper
  not held locally); and the two undetermined-coefficients comparative-static
  blocks (the $b^g_{H,s}$ block triangularity giving $dk/db^g_{H,s}=0$, and the
  $\rraF/\rra$ block with the $\lwedge>0$ requirement).

  \item \textbf{Section~\ref{sec:prop5} (Prop.~5), 3 flags.} The Prop.~5 statement
  (transcribed from the brief); the sign of the productivity coefficient
  $\propto\rra-\rraF$ (we supply the mechanism via the kernel-difference); and the
  sign of the safety coefficient $>0$ (we supply the comovement sign-chasing).

  \item \textbf{Section~\ref{sec:risksharing-specialness} (this WP), 9 flags.}
  (i) The Backus--Smith levels relation~\eqref{eq:bs-levels} (provenance from
  \eqref{eq:risk-sharing} at $\rra=\rraF=1$); (ii) the ERS/LOOP
  relation~\eqref{eq:loop-rel-raw}--\eqref{eq:loop-solved} (transcribed with the
  Backus--Smith substitution verified); (iii) the constant-overall-wealth-share
  reading at the $\rra=\rraF=1$ benchmark (supplied from the structure
  of~\eqref{eq:eq99}); (iv)--(vi) the three specialness arguments
  (zero net supply, country size, currency of invoicing --- all transcribed at KL's
  expository level, with mechanisms supplied but the extensions not formalized);
  (vii) the Foreign-only-demand multiplier
  result~\eqref{eq:b4-home-ratio}--\eqref{eq:b4-mu-omega} (we supply the
  FOC-division step giving $\mu_t=\cy_t$); (viii) the unchanged international
  risk-sharing conditions~\eqref{eq:b4-rs-safe}--\eqref{eq:b4-rs-cap} (transcribed);
  (ix) the entire B.5 distinct-capital / sticky-price summary (stated
  \emph{without proof}, as KL do).
\end{itemize}

\paragraph{Where the analytical content is thinnest.} Two places deserve explicit
warning for the extension worker. First, \textbf{App.~B.5} (distinct capital
stocks and sticky prices, Subsection~\ref{sec:b5}) is stated by KL \emph{without
proof}; we transcribe the analog Propositions~1--5 and the key new result --- the
ambiguous sign of the Home capital return~\eqref{eq:b5-rk-ambiguous} and the
definitive relative-return gap~\eqref{eq:b5-rk-gap} --- but a full re-derivation is
not available in the published material and is not attempted here. Second, the
\textbf{international-portfolio equation~\eqref{eq:eq99}} and its
$\Gamp$-augmented form~\eqref{eq:eq99-prime} are the densest collected results in
the appendix; KL display only the final form, and while every coefficient is
matched, the intermediate kernel-difference algebra is a genuine reconstruction.
The Propositions~4--5 conclusions depend only on the \emph{structure}
of~\eqref{eq:eq99} (which terms load on which shock, and the signs of their
coefficients), which is robust to any residual algebra in the exact magnitudes.

\subsection{Closing note}
\label{sec:closing}

This document is a faithful re-derivation of the analytical section of Kekre and
Lenel (2024, AER) --- their Section~II and online Appendix~B --- assembled as the
reference backbone for the big\_cy extension. It states KL's assumptions, results,
and intuition, fills in the algebra that the published appendix suppresses (flagged
throughout with \texttt{\textbackslash gapflag}), and indexes exactly where those
reconstructions occur. It takes \emph{no position} on the big\_cy extension itself:
the comparative-static reading of Propositions~4--5 around the risk-tolerance
asymmetry, and the separation of the safety channel from the risk-tolerance channel
in Proposition~\ref{prop:riskpremium}, are recorded here as KL's own results, to be
used as the starting point --- not the conclusion --- of the extension work.
